A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2024-10-09 manuscript/main.tex
linear and sine learning curves + manuscript
manuscript

\newpage
\textcolor{red}{Reorganize}
\begin{itemize}
	\item Abstract
	\item Introduction
	\item Methods
	\item Datasets
	\item Results
	\begin{itemize}
		\item Function fitting 
		\begin{itemize}
			\item Classical testing
			\item All (5 + 16 qubit)
			\item RUD + AL (5 + 16 qubit)
			\item Error mitigation
			\item Real device
		\end{itemize}
		\item BSE
		\begin{itemize}
			\item Classical testing
			\item All 5 qubit
			\item Truncated 16 qubit set (cost analysis 5 qubit)
			\item RUD + AL (5 + 16 qubit)
			\item Error mitigation
			\item Real device
		\end{itemize}		
		\item DDCC
		\begin{itemize}
			\item Classical testing
			\item Truncated  5 qubit set (based on BSE 5 qubit cost analysis)
			\item Truncated 16 qubit set (based on BSE 5 qubit cost analysis)
			\item RUD + AL (5 + 16 qubit)
			\item Error mitigation
			\item Real device
		\end{itemize}		
	\end{itemize}
	\item Discussion and Conclusion
\end{itemize}

@@

@@

\section{Conclusion}

Molecular representations specifically for QML
Distributed QC to incorporate more features

>>>>

\newpage
\textcolor{red}{Reorganize}
\begin{itemize}
	\item Abstract
	\item Introduction
	\item Methods
	\item Datasets
	\item Results
	\begin{itemize}
		\item Function fitting 
		\begin{itemize}
			\item Classical testing
			\item All (5 + 16 qubit)
			\item RUD + AL (5 + 16 qubit)
			\item Error mitigation
			\item Real device
		\end{itemize}
		\item DDCC (5 qubit only because classically it can be done with 5 features!)
		\begin{itemize}
			\item Classical testing
			\item Truncated  5 qubit set (based on BSE 5 qubit cost analysis)
			\item RUD + AL (5)
			\item Error mitigation
			\item Real device
		\end{itemize}
		\item BSE
		\begin{itemize}
			\item Classical testing
			\item All 5 qubit
			\item Truncated 16 qubit set (cost analysis 5 qubit)
			\item RUD + AL (5 + 16 qubit)
			\item Error mitigation
			\item Real device
		\end{itemize}				
	\end{itemize}
	\item Discussion and Conclusion
\end{itemize}

@@

A2 HWE-CZ
Performs better than all but 
\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{images/Function_Fitting/sine_learning_curves.png}
	\caption{sine learning curve}
	\label{fig:sine_learning_curves}
\end{figure}

@@

\section{Conclusion}
Depth is not always better!
Molecular representations specifically for QML
Distributed QC to incorporate more features
